\documentclass[a4paper,12pt]{report}
\title {Anholor - mainline story}
\author {Anholor developers}
\begin{document}
\maketitle
[Person wakes up inside his apartment house and sits in front of his TV. TV is showing a white noise screen. A six handed figure is shown in the TV.]\newline

[ECHO x Hibikase starts playing]\newline

[The person is pulled into the TV and lands in a World War - I warzone]\newline

[An option is given to the player to choose a name for the PC or take a random name; If the player chooses to enter a name, he/she is given enough space to enter a name. Else, he/she is given a random name]\newline

[In front of the player are two soldiers who are fighting a war. The soldier tosses a gun to the player and gives the player grenades and a first aid kit.]\newline

[Battle ensues]\newline

[If the player chooses to kill his comrades, he gets cursed by them.]\newline

[Battle continues]\newline

[The forces reach a walled city]\newline

[The player sees the soldiers climb to the top of the wall]\newline

[The player is given a choice. Does he want to climb the wall and annihilate the soldiers enemies or desert the battlefield and get out of the TV.]\newline

[If the player chooses to climb the wall, he gets met with soldiers dressed in black]\newline

Soldier in Black : Hail the furher!!! Death to our enemies!!\newline

[Soldier in greyish green talks to a person through the radio phone]\newline

Soldier in Black : Die Wargebaisha. Wanderich! Wanderich!\newline

Soldier in Black : Daisha! Daisha!\newline

Soldier in Black :  Nein! Nein! Nein! Nein!\newline

[The commanding soldier in black shoots the protesting soldier in black]\newline

Soldier in greyish green : What the shit Matthew? Why is he shooting his own?\newline

Another soldier in greyish green : I don't know sergeant.\newline

Sergeant : Matthew, you were in the CIA. You don't know that?\newline

Another soldier in greyish green : I don't know sergeant.\newline

Sergeant : Matthew, why are we fighting this war? Matthew, he is saying he is saying he is our brother. Our long lost brother. Matthew, don't shoot him.\newline

Another soldier in greyish green : Seargent, what do we do about this?\newline

Sergeant : Matthew, don't shoot. Don't shoot. Don't shoot.\newline

Commanding soldier in black : Sheit! Sheit! Sheit!\newline

Sergeant : Holy Shit Matthew!! Everybody take cover!!\newline

Commanding soldier in black : Kielick!! \newline

Soldier in black : Nein!\newline

[The commanding soldier in black shoots the soldier in black]\newline

Commanding soldier in black : Die Wargeshiem. Zur Maeishim.\newline

[The commanding soldier in black commits suicide by shooting himself in the head]\newline

Soldiers in black : Commerick!!\newline

Seargant : Matthew, call the medics. We are taking them to America. As for the dead soldiers. Take their insignia. We are burying them alongside them.\newline

Soldier in greyish green : Matthew, drag his corpse after we are done with this place. We are burying them.\newline

[The player gets pulled out of the TV with mixed feelings on what he saw]\newline

\end{document}